---
title: "Assignment #10"
author: "Ningqiao Li"
date: "April 19, 2020"
output: html_notebook
---

***
```{r include=FALSE}
library(tidyverse)
library(here)
```


### 1. Write a script to import and tidy the Johnson Elementary Project Data. 

```{r include=FALSE}
ELA <- read_csv("Johnson Elementary ELA Project.csv", skip = 3)
ELA

tidy.ELA <- ELA %>%
  fill(X1)

colnames(tidy.ELA)[1] <- "Room"

tidy.ELA <- tidy.ELA %>%
  separate('Tardies; Absences', into = c("Tardies", "Absences"), sep = ";", convert = TRUE)
tidy.ELA

colSums(is.na(tidy.ELA))

tidy.ELA2 <- tidy.ELA %>%
  drop_na(`Student ID`)  ## This one works.

write_csv(tidy.ELA2, "tidy.ELA2.csv")

```

```{r}
tidy.ELA <- tidy.ELA %>%
  filter(!is.na(`Student ID`))  ## It works.

tidy.ELA %>%
  filter(`Student ID` >0) ## It also works!
```


***

### 2. Write a script to provide summary statistics for the number of tardies and absences for each room.

```{r}
summary.stats <- tidy.ELA2 %>%
  group_by(Room) %>%
  summarize(T_mean = mean(Tardies),
            T_sd = sd(Tardies),
            A_mean = mean(Absences),
            A_sd = sd(Absences))
summary.stats

```


***

### 3. Write a script to show the frequency of missing data points for each quarter by room.

```{r}
frenq.missing <- tidy.ELA2 %>%
  group_by(Room) %>%
  summarize(sum(is.na(`1st Quarter`)),
          sum(is.na(`2nd Quarter`)),
          sum(is.na(`3rd Quarter`)),
          sum(is.na(`4th Quarter`)))
frenq.missing
```

***

### 4. Construct a graph that illustrates the median rating trends across the four quarters for the fifth-grade classes. 

```{r}

tidy.ELA3 <- tidy.ELA2 %>%
  gather(`1st Quarter`, `2nd Quarter`, `3rd Quarter`, `4th Quarter`,
         key = "Quarter",
         value = "Rating")

median_plot <- tidy.ELA3 %>%
  group_by(Room, Quarter) %>%
  summarize(median_score = median(Rating, na.rm = TRUE)) %>%
  ggplot(aes(x = Quarter, y = median_score, group = Room)) +
    geom_line (aes(color = Room)) +
    facet_wrap(vars(Room)) +
    labs(x = "Quarter", y = "Meidan ELA Ratings",
       title = "Median rating trends across different classes")

median_plot  
```


***

### 5. Use the NYC flights data to construct a graph that compares carriers in terms of the proportion of 2013 flights that arrived on time when traveling from New York City to Atlanta. Your graph should include a title and easy-to-read labels, including the names of airlines rather than airline codes. 

```{r}
# Tidy the data first
NYC <- read_csv("NYC Flights 2013.csv")
NYC
(NYC2 <- NYC %>%
     filter(origin == "JFK", dest == "ATL" ) %>%
     select(arr_delay, carrier, origin, dest))

```


```{r}
# Merge data to get the full name of carrier.
airlines <- read_csv("Airlines Data.csv")
NYC2 <- NYC2 %>%
  left_join(airlines, by = "carrier")
  
NYC2 <- NYC2 %>%
  mutate (on_time = (arr_delay <= 0)) %>%
  drop_na(on_time)

# Plot the graph

finalplot <- NYC2 %>%
  ggplot(aes(x = name, fill = on_time)) +
  geom_bar(position = "fill") +
  labs(x = "The name of Carrier", y = "Proportion",
       title = "Proportion of arriving on time by carrier")

finalplot
```


***
